Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-01-07 draft.tex
training description

@@

			each input feature. Further explanation is in the following section.

>>>>

		The dataset used for these experiments is the "In-the-Wild" dataset, one which focuses on
		the generalization of audio deepfake detection models by collecting real-world data, in
		comparison to other examples that use more controlled laboratory conditions
		\cite{muller_does_2022}.

@@

			each input feature. Further explanation is in the following section. Figure
			\ref{fig:model_plot} represents the layout of the model layers.
			\begin{figure}[htbp]
				\begin{center}
					\includegraphics[width=1\textwidth]{images/model_plot.png}
					\caption{The architecture of the model used for the experiment.}
					\label{fig:model_plot}
				\end{center}
			\end{figure}
			\subsubsection{Training and Evaluation}
			The black-box model described in the previous section was trained on the first 10,000
			samples out of the aforementioned dataset, with evaluation being performed on the
			remaining 21,778. Training batches consisted of 100 samples each with every window
			position for each sample and an upper limit of 1,000,000 lines per batch. For each
			batch, two epochs were performed. Because a single sample can have multiple input
			lines, evaluation cannot be performed on a per-line basis, but must instead be
			summarized. Two methods are possible: median and mean, with the difference in results
			being negligible in my experiments. The default threshold is 0.5, meaning that a
			result under 0.5 is a false result and over 0.5 is a true result. This threshold can
			however be adjusted, useful for computing the EER.
